---
title: "P8105_HW6"
author: Yijia Chen
date: 2021-12-4
output: github_document
---

```{r include = FALSE}
library(tidyverse)
library(viridis)
library(modelr)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# Problem 1
## Problem 1 (a)

Load and clean the child’s birthweight data

??menarche with 0????

```{r}
child_bw_df = 
  read_csv("data/birthweight.csv") %>% 
  mutate(
    babysex = factor(babysex),
    frace = factor(frace),
    malform = factor(malform),
    mrace = factor(mrace)
  )
```

Propose a regression model for birthweight base on baby’s head circumference at birth and baby’s length at birth

Check assumption of regression

```{r}
bhead_den = 
  child_bw_df %>% 
  select(bhead) %>% 
  ggplot(aes(x = bhead)) +
  geom_density()

blength_den = 
  child_bw_df %>% 
  select(blength) %>% 
  ggplot(aes(x = blength)) +
  geom_density()

bwt_den =
  child_bw_df %>% 
  select(bwt) %>% 
  ggplot(aes(x = bwt)) +
  geom_density()
```

Fit the model

Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

```{r}
model_1 = 
  lm(bwt ~ bhead + blength, data = child_bw_df) 

model1_des_plot =
  child_bw_df %>% 
  select(bhead, blength, bwt) %>% 
  relocate(bwt) %>% 
  add_predictions(model_1) %>% 
  add_residuals(model_1) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point()
```

## Problem 1 (b)

Compare your model to two others:

A. One using length at birth and gestational age as predictors (main effects only)
B. One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

Generate the A and B model

```{r}
train_df = sample_n(child_bw_df, 3500)
test_df = anti_join(child_bw_df, train_df)

```


```{r}
model_A = 
  lm(bwt ~ blength + gaweeks, data = child_bw_df)

model_B = 
  lm(bwt ~ babysex + bhead + blength + babysex * bhead + babysex * blength + bhead * blength + babysex * bhead * blength, data = child_bw_df)
```

